---
output:
  html_document:
    css: www/styles.css
    anchor_sections: FALSE
    includes:
      in_header: "header_manual.html"

params:
  year_curr: 2021 # Current year of sampling
  park: "ACAD"
  all_years: TRUE # If FALSE, only reports on year_curr; TRUE reports on all years
  
---
```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '', scipen = 100)
```

```{r imports, include = FALSE}
library(rockyIntertidal)
library(tidyverse)
library(knitr)
library(kableExtra)
library(htmltools) # for tagList

importData()
park = params$park
year_curr = params$year_curr
year = if(params$all_years == TRUE){2013:year_curr} else {year_curr}

# year = 2013:2021
# park = "ACAD"

arglist <- list(park = park, years = year)

locs <- do.call(getPIBoltDistance, arglist) |>
  select(Loc_Code) |> unique() |> c() #|> as.character()
```

Rocky intertidal Quality Control checking for `r params$park` and `r paste(year, collapse = ", ")` {.tabset .tabset-pills}
---

```{r, include = F, results = 'hide'}
source('park_QC_checks_compile.R')
```

```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE}
#---- Plotting bolt elevation by distance -----
trans_contour_plots <- 
  purrr::map(locs$Loc_Code, 
             ~plotPITransects(
               location = ., xlab = "Distance (m)", ylab = "Elevation MLLW (m)", title = TRUE, years = 2013:year_curr))

#---- Plotting species by elevation -----
trans_species_plots <- 
  purrr::map(locs$Loc_Code,
             ~plotPITransectSpecies(location = ., xlab = "Year", ylab = "Elevation MLLW (m)", 
                                    title = TRUE, years = 2013:year_curr, facet = T) +
    theme(legend.position = 'bottom',
          legend.text = element_text(size = 10),
          legend.key.size = unit(0.5, 'cm'),
          legend.key.width = unit(0.5, 'cm'),
          legend.key.height = unit(0.5, 'cm'),
          legend.title = element_blank()))

#---- Plotting photoplot cover by target species and site ----
photo_species_plots <- purrr::map(locs$Loc_Code,
  ~plotPhotoCover(location = ., top_spp = 3, years = 2013:year_curr)                                
  )

```


### QC Checks {.tabset}
#### Summary 

```{r}
QC_check_table
```

```{r echo = F, eval = include_visit_table, results = 'asis'}
cat("#### Compiled Notes", "\n")
if(include_visit_table == TRUE){
  visit_table
}
```

### Point Intercept Transects {.tabset}

```{r eval = pit_include, results = 'asis'}
cat("#### QC Checks", "\n")
```

```{r eval = pit_include}
check_null(miss_bolt_elev_dist)

check_null(later_bolt_dist_0)

check_null(bolt_check_tbl)
```

#### Transect Contour Plots {.tabset}

```{r warning = FALSE, message = FALSE, out.width='100%', out.height = '95%', results = 'asis'}
for(i in seq_along(locs$Loc_Code)){
   cat("##### ", locs$Loc_Code[[i]], "\n")
   print(trans_contour_plots[[i]])
   cat("\n\n")
}  
```

#### Transect Species Plots {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 12, fig.width = 10,  results = 'asis'}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n")
  cat("Point Intercept species by elevation. Points are median elevation across 3 transects. 
       Wider lines are the middle 25% and 75% quartiles. Thin lines are minimum and maximum elevations 
       recorded for a given species.", "\n")
  print(trans_species_plots[[i]])
  cat("\n\n") 
}
```

### Photoplots {.tabset}

#### QC Checks {.tabset}
```{r eval = photoplot_include, results = 'asis'}

check_null(photoplot_tbl)

check_null(spp_plot_tbl)
```

#### Photoplot Species Plots {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 12, fig.width = 10,  results = 'asis'}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n")
  cat("Species percent cover by target species group. Points are median cover across photoplots. 
       Error bars are minimum and maximum cover recorded within a target species. Only top 3 species
       are plotted in each target species group, with tied species included.", "\n")
  print(photo_species_plots[[i]])
  cat("\n\n") 
}
```

### Recruitment Plots

No checks added yet

### Temperature Loggers

No checks added yet

### Band Transects

No checks added yet
