---
output:
  html_document:
    css: www/styles.css
    anchor_sections: FALSE
    includes:
      in_header: "header_manual.html"

params:
  year_curr: 2021
  park: "ACAD"
  all_years: TRUE # If FALSE, only reports on year_curr; TRUE reports on all years
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '', scipen = 100)
```

```{r imports, include = FALSE}
library(rockyIntertidal)
library(tidyverse)
```

```{r imports2, include = FALSE, cache = T}
importData()
path = "../data/rocky/temp_data/Compiled_HT_water_temps/"
importWaterTemp(path = path, simplify = T, buoy = T)
```

```{r params, includ = FALSE}
# park = "ACAD"
# year_curr = 2021
# years = 2013:2021

test = TRUE

park = params$park
year_curr = params$year_curr
years = if(params$all_years == TRUE){2013:year_curr} else {year_curr}

# Set up args list
arglist <- list(park = park, years = years)

locs <- do.call(getPIBoltDistance, arglist) |>
  select(Loc_Code) |> arrange(Loc_Code) |> unique() |> c() #|> as.character()

trans_species <- do.call(getPISpecies, arglist) |> 
  select(Spp_Code) |> arrange(Spp_Code) |> unique() |> 
  filter(!Spp_Code %in% c("BOLT", "ROCK", "WATER", NA, "OTHSUB", "OTHINV", "UNIDEN")) |> 
  c()

trans_species_com <- switch(park, 
                            "ACAD" = c("ALGGRE", "ALGRED", "ARTCOR", "ASCEPI", "ASCNOD", "BARSPP", 
                                      "CHOMAS", "CRUCOR", "FUCEPI", "FUCSPP", "MUSSPP", "ULVLAC"),
                            "BOHA" = c("ALGGRE", "ALGRED", "ASCEPI", "ASCNOD", "BARSPP", 
                                       "CHOMAS", "FUCEPI", "FUCSPP", "ULVLAC")
                       )

```

Rocky intertidal data summary for `r params$park` and `r paste(years, collapse = ", ")` {.tabset .tabset-pills}
---

```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
#---- Plotting all species by elevation per location -----
trans_species_plots <- 
  purrr::map(locs$Loc_Code,
             ~plotPISpecies(location = ., xlab = "Year", ylab = "Elevation MLLW (m)", species = 'all',
                                    title = TRUE, facet = TRUE, years = years, rev_axis = F) +
    theme(legend.position = 'bottom',
          legend.text = element_text(size = 10),
          legend.key.size = unit(0.5, 'cm'),
          legend.key.width = unit(0.5, 'cm'),
          legend.key.height = unit(0.5, 'cm'),
          legend.title = element_blank()))
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
#---- Plotting individual PI transect species across all locations -----
trans_species_plots_park <- 
  purrr::map(trans_species_com, 
             ~ plotPISpecies(park = park, location = 'all', xlab = 'Year', ylab = "Elevation MLLW (m)",
                                     species = ., title = FALSE, facet = TRUE, years = years, rev_axis = F))
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
#---- Plotting main 5 species for PI transects with plotly -----
trans_spp_plotly <- plotPISpecies(park = park, years = years, title = F, xlab = NULL, #facet = F,
                      species = 'all', main_groups = T, rev_axis = F, plotly = T, ribbon = T)
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
#---- Plotting photoplot cover by target species and site ----
photo_species_plots <- purrr::map(locs$Loc_Code,
  ~plotPhotoCover(location = ., species = 'all', top_spp = 3, years = years)                                
  )
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
#---- Plotting individual photoplot target species across all locations
targ_spp <- switch(park, 
                   "ACAD" = c("Barnacle", "Fucus", "Ascophyllum", "Red Algae", "Mussel"),
                   "BOHA" = c("Barnacle", "Fucus", "Ascophyllum", "Red Algae"))
                   
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
photo_species_plots_park <- purrr::map(targ_spp,
  ~plotPhotoCover(park = park, location = 'all', target_species = ., 
                  top_spp = 3, species = 'all', years = years)                                
  )

```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE, eval = test}
photo_species_heatmap <- purrr::map(locs$Loc_Code,
  ~plotPhotoCover(park = park, location = ., heatmap = TRUE, main_groups = T, years = years))

```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE}
#---- Plotting water temp data by site -----
water_temp_plots <- purrr::map(locs$Loc_Code,
  ~plotWaterTemp(location = ., years = years, palette = 'black', plotly = T)
  )
```
```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE}
#---- Plotting water temp of all sites ----
water_temp_plots_year <- purrr::map(years,
  ~plotWaterTemp(park = park, location = 'all', years = ., palette = 'viridis',
                 facet = F, plotly = T))
```

```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE}
#---- Plotting buoy data of each years for a park ----
buoy_plots_year <- purrr::map(years, 
                              ~plotBuoyData(park = park, years = ., metric = 'all',
                                            facet_col = 1))
```


### Point Intercept Transects {.tabset}

#### By Main Species {.tabset}
Point Intercept species by elevation across locations. Points are median elevation across 3 transects. 
Bands lower 25% and upper 75% distributions across 3 transects for the primary species of concern. In the legend, Ascophyllum nodosum (Knotted wrack) is abbreviated as ASCNOD, Barnacles are abbreviated as BARSPP, Fucus spp. (Rockweed) is abbreviated as FUCSPP, Mussels are abbreviated as MUSSPP, and red algae are abbreviated as REDGRP. The red algae group includes Irish moss (Chondrus / Mastocarpus) and algae identified as Other Algae - Red. 
```{r fig.height = 8, fig.width = 10, eval = test}
trans_spp_plotly
```

#### By Location {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis', eval = test}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n")
  cat("Point Intercept species by elevation. Points are median elevation across 3 transects. 
       Wider lines are the middle 25% and 75% quantiles. Thin lines are minimum and maximum elevations 
       recorded for a given species.", "\n")
  print(trans_species_plots[[i]])
  cat("\n\n") 
}
```

#### By Species {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis', eval = test}
for(i in seq_along(trans_species_com)){
  cat("##### ", trans_species_com[[i]], "\n")
  cat("Point Intercept species by elevation across locations. Points are median elevation across 3 transects.
      Wilder lines are the middle 25% and 75% quantiles. Thin lines are minimum and maximum elevations
      recorded for a given species.", "\n")
  print(trans_species_plots_park[[i]])
  cat("\n\n")
}
```

### Photoplots {.tabset}

#### By Location {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis', eval = test}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n")
  cat("Species percent cover by target species group. Points are median cover across photoplots. 
       Error bars are minimum and maximum cover recorded within a target species. Only top 3 species
       are plotted in each target species group, with tied species included.", "\n")
  print(photo_species_plots[[i]])
  cat("\n\n") 
}
```

#### By Target Species {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis', eval = test}
for(i in seq_along(targ_spp)){
  cat("##### ", targ_spp[[i]], "\n")
  cat("Species percent cover by target species group across all lcoations. Points are median cover across photoplots. 
       Error bars are minimum and maximum cover recorded within a target species. Only top 3 species
       are plotted in each target species group, with tied species included.", "\n")
  print(photo_species_plots_park[[i]])
  cat("\n\n") 
}
```

#### Heatmaps {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 12, results = 'asis', eval = test}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n")
  cat("Median percent cover by target species group for main 5 species per photoplot target species. ", "\n")
  print(photo_species_heatmap[[i]])
  cat("\n\n") 
}
```


### Temperature Loggers {.tabset}
#### By Location {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis'}
for(i in seq_along(locs$Loc_Code)){
  cat("##### ", locs$Loc_Code[[i]], "\n\n")
  cat("\n")
  cat("Daily buoy and water temperature statistics for ", park, "and ", locs$Loc_Code[[i]], ".", "\n")
  cat("\n\n") 
    paste0("```{r fig.height = 10, fig.width = 10}\n\n",
           plotBuoyData(park = park, years = years, metric = 'all', facet_col = 1),
           cat("\n\n"),
           print(plotWaterTemp(location = locs$Loc_Code[[i]], years = years, palette = 'black', plotly = F)),
           cat("\n\n"),
           "```\n\n",
           cat("\n\n"))
  cat("\n\n")
  cat("\n\n")
  }
```

#### By Year {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10, results = 'asis', eval = T}
for(i in seq_along(years)){
  cat("##### ", years[[i]], "\n\n")
  cat("\n")
  cat("Daily buoy statistics for ", years[[i]], ".", "\n")
  cat("\n\n") 
    paste0("```{r fig.height = 10, fig.width = 10}\n\n",
           plotBuoyData(park = park, years = years[[i]], metric = 'all', facet_col = 1),
           cat("\n\n"),
           print(plotWaterTemp(location = 'all', years = years[[i]], plotly = F)),
           cat("\n\n"),
           "```\n\n",
           cat("\n\n"))
  cat("\n\n")
  cat("\n\n")
  }

```
