---
output:
  html_document:
    css: www/styles.css
    anchor_sections: FALSE
    includes:
      in_header: "header_manual.html"

params:
  year_curr: 2024 # Current year of sampling
  park: "ACAD"
  all_years: TRUE # If FALSE, only reports on year_curr; TRUE reports on all years
  
---
```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '', scipen = 100)
```

```{r imports, include = FALSE}
library(rockyIntertidal)
library(tidyverse)
library(knitr)
library(kableExtra)
library(htmltools) # for tagList

importData()
park = params$park
year_curr = params$year_curr
year = if(params$all_years == TRUE){2013:year_curr} else {year_curr}

# year = 2013:2021
# park = "ACAD"
# year_curr = 2021

arglist <- list(park = park, years = year)

locs <- do.call(getPIBoltDistance, arglist) |>
  select(SiteCode) |> unique() |> c() #|> as.character()
```

Rocky intertidal Quality Control checking for `r params$park` and `r paste(year, collapse = ", ")` {.tabset .tabset-pills}
---

```{r, include = F, results = 'hide'}
source('park_QC_checks_compile.R')
```

```{r, warning = FALSE, message = FALSE, results = 'hide', include = FALSE}
#---- Plotting bolt elevation by distance -----
trans_contour_plots <- 
  purrr::map(locs$SiteCode, 
             ~plotPITransects(
               site = ., xlab = "Distance (m)", ylab = "Elevation MLLW (m)", 
               title = TRUE, years = 2013:year_curr)) |> set_names(locs$SiteCode)

#---- Plotting species by elevation -----
trans_species_plots <- 
  purrr::map(locs$SiteCode,
             ~plotPISpecies(site = ., xlab = "Year", ylab = "Elevation MLLW (m)", 
                                    title = TRUE, years = 2013:year_curr, facet = T) +
    theme(legend.position = 'bottom',
          legend.text = element_text(size = 10),
          legend.key.size = unit(0.5, 'cm'),
          legend.key.width = unit(0.5, 'cm'),
          legend.key.height = unit(0.5, 'cm'),
          legend.title = element_blank())) |> set_names(locs$SiteCode)

#---- Plotting photoplot cover by target species and site ----
photo_species_plots <- purrr::map(locs$SiteCode,
  ~plotPhotoCover(site = ., top_spp = 3, years = 2013:year_curr, plotly = T)                                
  ) |> set_names(locs$SiteCode)


#---- Plotting motile invert counts by target species and site ----
motinv_species_plots <- purrr::map(locs$SiteCode,
  ~plotMotileInvertCounts(site = ., main_groups = TRUE, years = 2013:year_curr, 
                          plotly = T)) |> set_names(locs$SiteCode)

#---- Plotting motile invert measures by target species and site ----
motinv_meas_plots <- purrr::map(locs$SiteCode,
  ~plotMotileInvertMeas(site = ., years = 2013:year_curr)) |> 
  set_names(locs$SiteCode)

#---- Plotting echinorderm counts by site
echino_cnt_plots <- purrr::map(locs$SiteCode,
  ~plotEchinoCounts(site = ., years = 2013:year_curr, plotly = T)) |> set_names(locs$SiteCode)

echino_meas_plots <- purrr::map(locs$SiteCode,
  ~plotEchinoMeas(site = ., years = 2013:year_curr)) |> set_names(locs$SiteCode)

```


### QC Checks {.tabset}
#### Summary {.tabset}
```{r}
QC_check_table
```

```{r echo = F, eval = include_visit_table, results = 'asis'}
cat("#### Compiled Notes", "\n")
if(include_visit_table == TRUE){
  visit_table
}
```

### Point Intercept Transects {.tabset}
```{r eval = pit_include, results = 'asis'}
cat("#### QC Checks {.tabset}", "\n")
```

```{r eval = pit_include}
check_null(miss_bolt_elev_dist)

check_null(later_bolt_dist_0)

check_null(nonchron_bolt_dist)

check_null(missing_bolts)

check_null(short_trans)

check_null(long_trans)

check_null(bolt_check_tbl)
```

```{r warning = FALSE, message = FALSE, out.width='100%', out.height = '95%', results = 'asis', eval = F}
cat("#### Transect Contour Plots {.tabset}")
for(i in seq_along(locs$SiteCode)){
   loc <- locs$SiteCode[[i]]
   cat("##### ", loc, "\n")
   print(trans_contour_plots[[loc]])
   cat("\n\n")
}  
```


```{r warning = FALSE, message = FALSE, fig.height = 12, fig.width = 10,  results = 'asis', eval = F}
cat("#### Transect Species Plots {.tabset}")
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Point Intercept species by elevation. Points are median elevation across 3 transects. 
       Wider lines are the middle 25% and 75% quartiles. Thin lines are minimum and maximum elevations 
       recorded for a given species.", "\n")
  print(trans_species_plots[[loc]])
  cat("\n\n") 
}
```

### Photoplots {.tabset}
```{r include = F, results = 'hide'}
# Nesting substrate and motile inverts within photoplots
photoplot_eval <- ifelse(photoplot_include == TRUE | photoplot_mi_include == TRUE, TRUE, FALSE)
```

```{r eval = photoplot_eval, results = 'asis'}
cat("#### QC Checks {.tabset}", "\n\n")
```

```{r eval = photoplot_include, results = 'asis'}
cat("##### Substrate {.tabset}", "\n\n")
cat("<details open><summary class = 'drop'>", "<h3>Missing or duplicated photoplot scores</h3>", "</summary>")
check_null(photoplot_tbl)
cat("</details>")

cat("<details open><summary class = 'drop'>", "<h3>Years missing photoplot scores</h3>", "</summary>")
check_null(photoplot2_tbl)
cat("</details>")

cat("<details open><summary class = 'drop'>", "<h3>Missing or duplicated photoplot % cover for species recorded perviously</h3>", "</summary>")
check_null(spp_plot_tbl)
cat("</details>")

cat("<details open><summary class = 'drop'>", "<h3>Total % Cover sums to > 100%</h3>", "</summary>")
check_null(pctcov_sum_tbl)
cat("</details>")

```

```{r eval = photoplot_mi_include, results = 'asis'}
cat("##### Motile Inverts {.tabset}", "\n\n")
cat("<details open><summary class = 'drop'>", "<h3>Motile Invert. Counts</h3>", "</summary>")
check_null(micnt_nas_tbl)

check_null(micnt_99dam_tbl)

check_null(micnt_99nodam_tbl)

cat("<details open><summary class = 'drop'>", "<h3>Motile Invert. Measurements</h3>", "</summary>")
check_null(mimeas_nas_tbl)

check_null(mimeas_99.9_tbl)

check_null(mimeas_99_tbl)

check_null(mimeas_0_tbl)

cat("</details>")

```

#### Substrate Species Plots {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12,  results = 'asis'}
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Species percent cover by target species group. Points are median cover across photoplots. 
       Error bars are middle 50% cover recorded within a target species. Only top 3 species
       are plotted in each target species group, with tied species included.", "\n")
  cat(knit_print(photo_species_plots[[loc]]))
  cat("\n\n") 
}
```

```{r include = F}
htmltools::tagList(photo_species_plots)
# note that this has to be here for the previous code to knit, even though results aren't included in report.
```

#### Motile Invert. Counts {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12,  results = 'asis'}
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Motile invertebrate count data showing the median count across photoplots as the points. 
       Error bars are middle 50% distribution of counts recorded within a target species. ", "\n")
  cat(knit_print(motinv_species_plots[[loc]]))
  cat("\n\n") 
}
```

```{r include = F}
htmltools::tagList(motinv_species_plots)
# note that this has to be here for the previous code to knit, even though results aren't included in report.
```

#### Motile Invert. Measurements {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12,  results = 'asis'}
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Motile invertebrate measurement data across years. ", "\n")
  print(motinv_meas_plots[[loc]])
  cat("\n\n") 
}
```


### Echinoderms {.tabset}
```{r eval = echino_include, results = 'asis'}
cat("#### QC Checks {.tabset}", "\n\n")
cat("<details open><summary class = 'drop'>", "<h3>Echinoderm Counts</h3>", "</summary>")
check_null(eccnt_nas_tbl)

check_null(eccnt_99_tbl)

cat("<details open><summary class = 'drop'>", "<h3>Echinoderm Measurements</h3>", "</summary>")
check_null(ecmeas_nas_tbl)

check_null(ecmeas_99.9_tbl)

check_null(ecmeas_99_tbl)

check_null(ecmeas_0_tbl)

cat("</details>")

```

#### Echinoderm Counts {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12,  results = 'asis'}
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Echinoderm count data showing the median count across photoplots as the points. 
       Error bars are middle 50% distribution of counts recorded within a target species. ", "\n")
  cat(knit_print(echino_cnt_plots[[loc]]))
  cat("\n\n") 
}
```

```{r include = F}
htmltools::tagList(echino_cnt_plots)
# note that this has to be here for the previous code to knit, even though results aren't included in report.
```

#### Echinoderm Measurements {.tabset}
```{r warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12,  results = 'asis'}
for(i in seq_along(locs$SiteCode)){
  loc <- locs$SiteCode[[i]]
  cat("##### ", loc, "\n")
  cat("Echinoderm measurement data across years. ", "\n")
  print(echino_meas_plots[[loc]])
  cat("\n\n") 
}
```


### Recruitment Plots

No checks added yet

### Temperature Loggers

No checks added yet


